---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gnonadd

<!-- badges: start -->
<!-- badges: end -->

`gnonadd` is a package accompanying the paper [Complex effects of sequence variants on lipid levels and coronary artery disease](https://www.sciencedirect.com/science/article/pii/S0092867423009017?dgcid=coauthor) published in Cell September 2023. The package is intended to properly document the conducted analysis and aid researchers in studying various non-additive models.

## What is in the package?

The goal of the `gnonadd` package is to simplify workflows with non-additive 
analysis in genetic associations.

This includes e.g.

1) Variance effects
2) Correlation effects
3) Interaction effects
4) Dominance effects

## Included Functionality

The following is a non-comprehensive summary of the included functions:

- `alpha.calc` function to compute multiplicative variance effects
- `alpha.cond` function to do conditional analysis of variance effects
- `kappa_calc` function to compute correlation effects (gt/pheno/pheno)
- Correlation calibration
- `Var.assoc` Testing variance scores associations with data
- Dominance effect model implementation
- Interaction effect model (gt/gt/pheno) (genotype interaction) implementation
  - Pairwise genotype interaction implementation for list of genotypes
- Interaction effect model (gt/pheno/pheno) (environment interaction) implementation
  - Environment interaction cross of lists of phenotypes and genotypes (single outcome phenotype)
- Function to create traditional genetic score
- Function to create traditional genetic score with interaction effects as well
- Function to create traditional genetic score with interaction effects and dominance effects as well
- Function to create variance genetic score
- Summary visualizations
- Histograms by genotype

Please refer to the documentation for examples with simulated data.

## Installation

You can install the latest version of the package via the `remotes` package:

```{r, eval = FALSE}
# Use remotes:
remotes::install_github("DecodeGenetics/gnonadd")
```

The current version on CRAN can be installed with:

```{r, eval = FALSE}
install.packages("gnonadd")
```

## Citing this package

For citing this package, please use the following source:

```{r, eval = TRUE}
citation("gnonadd")
```
